% resume.tex
% vim:set ft=tex spell:

\documentclass[10pt]{article}
\usepackage[letterpaper, top=.2in, bottom=.2in, left=.5in, right=.5in]{geometry}
\usepackage{mdwlist}
\usepackage{hyperref}

\usepackage{fontspec}
\setmainfont{Times New Roman}

% \usepackage[T1]{fontenc}
% \usepackage{textcomp}
% \usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}



% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}




% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{YUCHEN WANG\\
\ }}
	\headerrow
	{(573) 239-5737}
	{2500 OLD HWY 63 S, APT 823}
	\\
	\headerrow
	{\href{mailto://yuchen.wang@mizzou.edu}{yuchen.wang@mizzou.edu}}
	{COLUMBIA, MO, 65201}
\end{center}


% \hrule
% \vspace{-0.4em}
% \subsection*{\centering OBJECTIVE}
% 
% Lorem ipsum dolor sit amet, consectetuer


\hrule
\vspace{-0.4em}


\subsection*{\centering EDUCATION}

\headerrow
	{\textbf{M.A.~in Statistics}}
	{\textbf{Jan 2014 – Present}}
\\
\headerrow
	{Department of Statistics, University of Missouri-Columbia}
	{Missouri, U.S.}
\\
\headerrow
	{\textbf{B.S.~in Statistics}}
	{\textbf{Sep 2009 – Jun 2013}}
\\
\headerrow
	{Department of Statistics and Actuarial Science, East China Normal University}
	{Shanghai, China}
\\
\headerrow
	{\textbf{Minor (36 credits) in Computer Technology and Application}}
	{\textbf{Feb 2011 – Jun 2013}}
\\
\headerrow
	{Department of Computer Science and Engineering, Shanghai Jiao Tong University}
	{Shanghai, China}
\\


\hrule
\vspace{-0.4em}



\subsection*{\centering PROFESSIONAL EXPERIENCE}
\begin{unindentsection}{\parindent}
	% {\parindent}
% \hyphenpenalty=1000
\begin{itemize}
	\item
	\headerrow
		{\textbf{Research Assistant, East China Normal University, Shanghai}}
		{\textbf{Jul 2012 – Dec 2013}}
		\indent Research on theories and applications of statistical process control,
		with focus on an applied project of quality control in tobacco
		production. In charge of the control problem of a tobacco
		dehumidification process, the most critical control unit among all
		tobacco production processes.
	\begin{itemize*}
		\item
		Facing statistical problems like: multivariate regression with time-lag, high
		frequency time series, clustered data, contaminated data and non-normal
		residual.
		\item
		Developer of an R package which contains all statistical algorithms,
		data cleaning and visualization methods used in the project.
		\item
		Two papers were finished (unpublished): one is on semi-parametric
		regression model for clustered data and another is on ridge estimator
		in multivariate regression with correlated covariates.
	\end{itemize*}
	
	\item
	\headerrow
		{\textbf{Operations and Maintenance Intern, Digital Resource, Shanghai}}
		{\textbf{Jan 2011 – Feb 2011}}
	\indent Responsible for the operation and maintenance for Shanghai Testing
	Center's information system. Participated in building the information
	infrastructure for Advanced Financial School of Shanghai Jiao Tong
	University. Got knowledge and experience with Internet and computer
	science.
	
	\item	
	\headerrow
		{\textbf{Analyst Intern, Shanghai Association for Quality, Shanghai}}
		{\textbf{Jul 2010 – Aug 2010}}
	\indent Planned and conducted the customer satisfaction survey sampling for the
	Xujiahui business circle. Responsible for street interview, data entry,
	collation, analysis and reporting writing, pretty much the whole cycle
	of survey sampling.
\end{itemize}
\end{unindentsection}

	
\hrule
\vspace{-0.4em}
\subsection*{\centering PROFESSIONAL SKILLS}

\begin{description*}
	\item[Statistical Computing:] Outstanding skills in R. Developer and maintainer of a CRAN package \emph{jtrans}. More repos on my GitHub: \url{http://www.github.com/wangyuchen}. Proficient in SAS and SPSS for standard statistical analysis.
	\item[Mathematical Modeling:] Adept in MATLAB and LINGO during Mathematical Contest in Modeling. Experience with Octave and Gnuplot during the \emph{Machine Learning} course on Coursera.
	\item[Operating Systems:] Strong interest in Unix-like systems, especially in the aspect of server management. Builder and administrator of the high-performance computing cluster for the School of Finance and Statistics, ECNU, which provides cloud computing environment of R and MATLAB.
	\item[General Purpose Programming:] Extensive object-oriented programming experience with \CPP. Experience with Java.
	\item[Specialities in Statistics:] Semi-parametric models; longitudinal data; Time series Analysis; Bayesian analysis; Nonparametric methods and other computationally intensive statistical methods.
	\item[Web:] Web data crawler; Spatial analysis and geocoding; Web-based data visualization using interactive plots; Experience with HTML and CSS; Blog in Jekyll and builder of \url{http://www.biostat.com.cn}; 
	\item[Others:] Effective in \emph{knitr}, in which I can combine my favorite markup languages (Markdown/\LaTeX) with code/outputs produced by a script language (R).
\end{description*}

\hrule
\vspace{-0.4em}
\subsection*{\centering TALKS AND HONORS}


\begin{unindentsection}{\parindent}
	\begin{itemize}
		\item
		\headerrow
			{\emph{Say Goodbye to Copy and Paste in Statistical Analysis}, $1^{st}$ R salon, East China Normal University}
			{\textbf{Dec 18, 2013}}
		\item
		\headerrow
			{\emph{Conducting Meta-analyses}, School of Finance and Statistics, East China Normal University}
			{\textbf{May 15, 2013}}
		\item 
		\headerrow
			{\emph{R and Object-oriented Statistical Analysis}, $5^{th}$ China-R Conference, Shanghai}
			{\textbf{Nov 4, 2012}}
		\item 
		\headerrow
			{\textbf{Successful Participant}, Mathematical Contest in Modeling, COMAP}
			{\textbf{Mar 2012}}
		\item
		\headerrow
			{\textbf{Third Price}, Mathematical Contest in Modeling, East China Normal University}
			{\textbf{Oct 2011}}
		
	\end{itemize}
\end{unindentsection}


\end{document}
