\documentclass[11pt]{article}

\usepackage[letterpaper, margin=.95in]{geometry}
\usepackage{mdwlist}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{fontspec}
\usepackage[compact]{titlesec}

\pagestyle{empty}
\setlength{\skip\footins}{.3em}

\setmainfont{Times New Roman}

\linespread{1.15}


% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 & #2 \\
\end{tabular*}
}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{0em}\raisebox{.12ex}{\footnotesize\bf ++}}

% enumitem setup
\setlist[description]{nolistsep, leftmargin=\parindent,	labelindent=.33\parindent, rightmargin = .33\parindent}

\setlist[itemize]{nolistsep, rightmargin = .33\parindent}

% and the actual content starts here
\begin{document}

\begin{center}
	\huge\textbf{YUCHEN WANG}
\end{center}
\noindent\headerrow{+1 (573) 239-5737}{30 Gardner Road, Apartment 4F}
\headerrow{\href{mailto:ycwang0712@gmail.com}{ycwang0712@gmail.com}}{Brookline, Massachusetts, 02445}

\vspace{-.8em}
\hrule


\subsubsection*{\centering RELEVANT EXPERIENCE}
\vspace{-.3em}


\headerrow
{\textbf{Associate Director, Marketing Science}, In4mation Insights, Massachusetts}
{\textbf{September 2015 – Present}}
\begin{itemize}
		\item Led a team of 4 analysts, in charge of day-to-day communication with clients and statistical analysis and software development for marketing, product development, and regulartory requests.
		\item Participated in projects of market structure, segmentation, and choice modeling; experienced in advanced models like hierarchical Bayesian models, structural equation models, latent class clustering, and nested logit regressions.
    \item Developed a scoring system for product superiority by borrowing ideas from spatial statistics, which was then widely used for over 30 products.
    \item Developed dashboards for standardized statistical analysis on public health databases in \emph{Shiny} and \emph{R}.
\end{itemize}



\noindent\headerrow
{\textbf{Research Assistant}, University of Missouri-Columbia, Missouri}
{\textbf{August 2014 – May 2015}}
\noindent\begin{itemize}
    \item Worked with Ph.D. students on Bayesian computation problems. By caching candidate samples in a low-acceptance MCMC algorithm and vectorization (\emph{Fortran}), I sped up the algorithm by 30x and developed it into the MethyBayes package (\href{https://cran.rstudio.com/web/packages/MethyBayes/index.html}{R-CRAN}).
    \item Parallelized a large-scale Bayes factor computation program (\emph{Fortran}) using both \emph{OpenMP} and \emph{MPI}; Tuned for distributed computing on different kinds of high-performance computing clusters to achieve the best performance.
\end{itemize}




\noindent\headerrow
{\textbf{Research Assistant}, East China Normal University, Shanghai, China}
{\textbf{June 2012 - July 2014}}
\noindent\begin{itemize}
    \item Participated in a statistical process control project for tobacco manufacturing. Developed quality control models for high-frequency data (GBs/hour) based on a semi-parametric regression model.
    % \item Led a group of 4 members, designed an interactive web application for a sequential experimental design procedure (\emph{R}/\emph{Shiny}).
\end{itemize}


% 	\item Joined a research team of Statistical Process Control (SPC) in tobacco manufacturing as a part-time research assistant.
% 	\begin{itemize}
% 		\item The only undergraduate student in a research team of 7 members consisting graduate students and faculties.
% 		\item Experienced in analyzing real-world big data (GBs per hour) from observational studies on Amazon EC2 using parallelized algorithms.
% 		\item Designed a control scheme for controlling tobacco dehumidification process, which is the most critical and complicated control unit among all tobacco manufacturing processes.
% 		\item Collaborated with both quality control team at the tobacco manufacturing factory and software engineering team of an IT company. The final quality control product could precisely detect abnormalities of the manufacturing in advance so as to minimize the cost of failure products.
% 	\end{itemize}
%
% 	\item Hired as a full-time research assistant in charge of the SPC project after graduation. Led a team of 21 members.
% 	\begin{itemize}
% 		% \item Mentored 7 members in the team. Trained all new members about previously used models and programs.
% 		\item Developed an R package for the project containing raw data, data cleaning routines, statistical algorithms and visualization tools. Programmed over 2,500 lines of R code for this project.
% 	\end{itemize}
%
% % 	\item Recruited 3 undergraduate students for the development of a statistical software with user interface as a product for a two stage randomized experiment project.
% % 	\begin{itemize}
% % 		\item Worked remotely with the rest of the team while studying abroad.
% % 		\item Designed and developed an interactive data visualization web application in R and \emph{Shiny}.
% % 	\end{itemize}
% \end{itemize}


\vspace{.5em}
\hrule

\subsubsection*{\centering EDUCATION}
\vspace{-.3em}

\headerrow
	{\textbf{\emph{Master of Arts} in Statistics}, University of Missouri}
	{\textbf{January 2014 - July 2015}}
	\begin{itemize}
		\item GPA 3.9 with A+ in Probability Theory, Advanced Linear Models and Bayesian Statistics.
		\item Took research credits in spatial statistics; developed sppmix package  (\href{https://github.com/wangyuchen/sppmix}{GitHub}) for fitting Bayesian mixture models to spatial point patterns.
	\end{itemize}
\noindent\headerrow
	{\textbf{\emph{Bachelor of Science} in Statistics}, East China Normal University}
	{\textbf{September 2009 - June 2013}}
	\begin{itemize}
	% 	\item Took \emph{Coursera} courses CS50, machine learning, high performance computing, etc.
		\item Nominated for best Bachelor's thesis: \textit{Residual Control Charts based on Semi-parametric Regression Models}.
	\end{itemize}
\noindent\headerrow
	{\textbf{\emph{Minor} (36 credits) in Computer Science}, Shanghai Jiao Tong University}
	{\textbf{February 2011 - June 2013}}
	% \begin{itemize}
	% 	\item Completed all undergraduate curriculum of Computer Science and a graduation thesis.
	% \end{itemize}


	\vspace{-.8em}
	\hrule

	\subsubsection*{\centering RELATED SKILLS}
	\vspace{-.3em}

	\begin{description}
		\item[Specialities in Statistics] Advanced knowledge in mathematical statistics and statistical learning models for regression and classification; sklled in generalized linear mixed models; conversant with Bayesian statistics and its computations; familiar with spatial point pattern models.
		\item[Languages and Softwares] Expert in \emph{R} with 8+ years of experience. Author of 15+ \emph{R} packages (GitHub: \href{https://www.github.com/wangyuchen}{@wangyuchen}); proficient in \emph{dplyr} and other \emph{tidyverse} packages.
		% \item[General Purpose Programming] Solid understanding of object-oriented programming. Experience in integrating \emph{\CPP} and \emph{Fortran} into \emph{R} packages. Extensive parallel computing experience in \emph{OpenMP} and \emph{MPI} with \emph{Fortran}. Proficient in \emph{MATLAB}.
		% \item[Operating Systems] Everyday Linux (Cent OS) user; \emph{VIM} user. Responsible for HPC cluster management at ECNU.
	\end{description}

\let\thefootnote\relax\footnote{Last update on \today}

\end{document}
